---
title: "Does height decide income?"
output:
  pdf_document: default
  html_document:
    df_print: paged
  word_document: default
---

```{r setup, echo = FALSE}
library(modelr)
library(ggplot2)
library(knitr)
library(tinytex)
library(tidyverse)
library(ggpubr)
```

## Introduction

It has been claimed that the height of a person is one of the most deciding factors for the persons income. In this short paper we will investigate this assertion by using a dataset from the _National Longitudinal Study_ (U.S. Bureau of Labor Statistics). See `help(heights, package = modelr)`for details.

## Summary statistics

We start by grouping the heights in 8 intervals and report summary statistics.

```{r}
heights$heightInt <- cut(heights$height, breaks = 8)
kable(summary(heights[,1:4]))
kable(summary(heights[,5:9]))
```

## Plots

```{r plot-height-income,  out.width="50%"}
ggplot(heights, mapping = aes(x = height, y = income)) +
  geom_point()
```

```{r}
heightsPosInc <- subset(heights, income > 0)
ggplot(heightsPosInc, mapping = aes(x = heightInt, y = income)) +
  scale_y_continuous(trans = scales::log_trans()) +
  geom_boxplot()
```

```{r}
heightsPosInc <- subset(heights, income > 0)
ggplot(heightsPosInc, mapping = aes(x = height, y = income)) +
  scale_y_continuous(trans = scales::log_trans()) +
  geom_point(position = "jitter") +
  geom_smooth(method = 'lm')
```

```{r}
heightsPosInc <- subset(heights, income > 0)
ggplot(heightsPosInc, mapping = aes(x = height, y = income)) +
  geom_point(position = "jitter") +
  geom_smooth(method = 'lm')
```

## How much do we earn extra per inch

```{r}
summary(lm(income ~ height, data = heights))
```

```{r}
library(dplyr)
my_data <- modelr::heights
my_data_fem <- my_data %>% dplyr::filter(sex=="female")
my_data_male<- my_data %>% dplyr::filter(sex=="male")


```

```{r}
ggmen <- ggplot()+
  geom_point(data=my_data_male, mapping=aes(x=height, y=income, colour="blue"))
ggwomen <- ggplot()+
  geom_point(data=my_data_fem, mapping=(aes(x=height, y=income, colour="yellow")))
```


```{r}
ggarrange(ggmen, ggwomen, labels = c("ggmen", "ggwomen"), colour = "blue", nrow = 1)
```

```{r}
sex <- pull(my_data[, 6])
ggplot() +
  geom_point(data = my_data, mapping = aes(x = height, y = income), colour = factor(ifelse(sex == "male", "blue", "red")), alpha = 0.4, shape = factor(ifelse(sex == "male", "male", "female")), size = 3) +
  labs(colour = "marital", shape = "sex", alpha = "height/income")
```

```{r}
ggplot() +
  geom_point(data = my_data, mapping = aes(x = height, y = income), colour = factor(if_else(my_data$sex == "male", "blue", "red")), alpha = 0.4, shape = factor(if_else(my_data$sex == "male", "male", "female")), size = 3) +
  labs(colour = "marital", shape = "sex", alpha = "height/income")
```


### Conclusion

One extra inch (2,72 cm) gives you $2982 extra income per year.
**You should have eaten your vegetables**, as your mother told you.
